---
title: "AnvBiocFHIR -- FHIR demonstrations with AnVIL"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{AnvBiocFHIR -- FHIR demonstrations with AnVIL}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    number_sections: yes
    toc: yes
---

# Introduction

This package uses pyAnVIL and SMART FHIR python infrastructure to work with
FHIR resources in AnVIL.

# FHIR stores

```{r do1}
library(AnvBiocFHIR)
allst = list_stores()
length(allst)
head(allst)
```

## Resources in a store

```{r lkres}
rgru = store_resources(tail(allst)[1])
length(rgru)
class(rgru[[1]])
```
A store has one or more ResearchStudy instances.

```{r lklk}
sapply(allst[1:4], function(x)length(store_resources(x)))
```

Methods for an instance.
```{r lkm}
names(rgru[[1]])
```

## Patients in a FHIR store

### Listing and counting

```{r dopats}
p1 = anv_fhir_test_list_patients(anvurl("phs001272-DS-CSD-MDS"))
p1$title
length(p1$pats)
names(p1$pats[[1]])
```

There are many available fields, but few are actually populated.
```{r lkfff}
names(p1$pats[[1]]$as_json())
```

### Multicore operations

We can dispatch to cluster nodes but must serialize all results
before returning.  To illustrate we define a
function that counts patients (up to 1000, until pagination
is straightened out) in a store:

```
countpats = function (x) 
{
    y = anv_fhir_test_list_patients(anvurl(x))
    ans = length(y$pats)
    names(ans) = y$title
    ans
}
```
No python references are returned.


We won't test this in this document, but this is a typical
result:
```
> system.time(pp <- lapply(allst[2:5], countpats))
   user  system elapsed 
 11.474   0.802  16.643 
> library(parallel)
> options(mc.cores=4)
> system.time(pp2 <- mclapply(allst[2:5], countpats))
   user  system elapsed 
 12.353   1.393   6.106 
```
